{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-15 brains-protocol.tex
Redo correlation talk

\rk{Correlation talk needs to be redone for new set of features}

Age of acquisition is a key variable which appears as a usual suspect in psycholinguistic studies and is also usually correlated to many of the other variables.
This relates to an ongoing debate suggesting that age of acquisition encodes a variety of phenomena, difficult to disentangle from more specific phenomena which could be captured by more independent variables~\CN{}.
Here however, as can be seen in Figure~\ref{fig:feature-corrs-initial}, age of acquisition has a relatively low correlation to the other variables (absolute value not above $0.42$ if we exclude the centrality measures), leading us to keep the variable in the rest of the analysis.

Number of phonemes and number of syllables naturally exhibit a strong linear correlation ($0.83$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.

Frequency and number of meanings both have relatively low levels of correlation to the other variables; we therefore also keep them in the rest of the analysis.

\bigskip
Network properties, on the other hand, are strongly dependent on one another.
As mentioned earlier, word degree and word pagerank have a very strong correlation ($0.89$) and, degree being generally more correlated to other variables, we chose to remove this variable from the results presented.
Finally betweenness centrality also exhibits strong correlation levels to the other network properties ($0.62$, $0.64$, and $0.72$ in absolute value), leading us to drop this final feature due to its redundancy.

>>>>

Number of phonemes and number of syllables naturally exhibit a strong linear correlation ($0.8$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.

Age of acquisition is a key variable which appears as a usual suspect in psycholinguistic studies.
Despite it being usually difficult to disentangle from many of the other variables, it is known to have independent effects, which is consistent with what we see in Figure~\ref{fig:feature-corrs-initial}: age of acquisition has a limited correlation to the other variables (absolute value not above $0.39$ if we exclude the number of syllables and the network properties), leading us to keep the variable in the rest of the analysis.

Frequency and number of synonyms both have relatively low levels of correlation to the other variables (excluding again the network properties); we therefore also keep them in the rest of the analysis.

\bigskip
Network centrality properties, on the other hand, are strongly dependent on one another.
As mentioned earlier, degree centrality and pagerank have a very strong correlation ($0.85$), and are also redundant with betweenness centrality (with correlation levels at $0.75$ and $0.68$ respectively).
Furthermore, the three variables are also strongly related to age of acquisition, which leads us to keep the latter as the sole indicator for centrality.

Conversely, clustering coefficient exhibits low correlation levels with all the variables we kept (maximum absolute value $0.38$), leading us to include it in the rest of the analysis.
